Effect of metabolic state on \textit{Paraclostridium bifermentans} surface properties and the implications for lead removal

### 2021-10-27 Writeup/Catalysts/MDPI_template/template.tex
Minor tweaks to intro, added new sources.

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, and has been shown to remove up to 93~\% of Pb(II) from solution \cite{Brink2017} by precipitating it out as PbS and Pb(0) \cite{Brink2020}. Following kinetic studies on the consortium, H\"orstmann et al. \cite{Horstmann2020c} proposed a two-phase exponential decay model to describe Pb(II) removal and attributed an initial rapid phase to adsorption. Subsequent research investigated this attribution by demonstrating that significant Pb(II) removal with the consortium took place following sterilization with NaN\textsubscript{3} \cite{VanVeenhuyzen2021}, highlighting the involvement of adsorption as a rather than the metabolically dependent precipitation.

@@

Several authors have noted that heavy metal onto living bacteria is noteably lower than on living
\cite{Hu2020,Mera1992,Johnson2007a}

@@

% Titrations

>>>>

A consortium of bacteria has been isolated from lead-contaminated soil at a battery recycling plant in Gauteng, South Africa, and has been shown to remove up to 93~\% of Pb(II) from solution \cite{Brink2017} by precipitating it out as PbS and Pb(0) \cite{Brink2020}. Following kinetic studies on the consortium, H\"orstmann et al. \cite{Horstmann2020c} proposed a two-phase exponential decay model to describe Pb(II) removal and attributed an initial rapid phase to adsorption. Subsequent research investigated this attribution by demonstrating that significant Pb(II) removal with the consortium took place following sterilization with NaN\textsubscript{3} \cite{VanVeenhuyzen2021}, highlighting the involvement of adsorption as a mechanism rather than the metabolically dependent precipitation.

@@

Several authors have noted that heavy metal adsorption onto living bacteria is noteably lower than on living
\cite{Hu2020,Mera1992,Kemper1993,Johnson2007a}

@@

% Titrations & Surface Charge
